
import package
```{r}
library(dplyr)
library(sos)
library(tidyverse)
library(sqldf)
library(RColorBrewer)	
library(leaps)
library(mlbench)
library(caret)
library(randomForest)
library(MASS)
library(pROC)
library(rpart)
library(datapasta)
library(tree)
library(ade4)
library(caTools)
library(rpart)	
library(rpart.plot)
library(rattle)
library(party)					# Alternative decision tree algorithm
library(partykit)
library(caret)	
library(ISLR)
library(glmnet)
library(corrplot)
library(MLmetrics)
library(reshape2)
library(randomForest)
library(car)
library(scales)
library(treemap)
library(plotly)
library(e1071)
library(xgboost)
library(class)
library(naivebayes)
```

import dataset
```{r}
data <- read.csv("cleaned_data.csv")
data <- data %>%
  dplyr::select(-c(reservation_status_date))
data
```

```{r}
set.seed(123)
training.samples <- data$is_canceled %>% 
  createDataPartition(p = 0.8, list = FALSE)
train.data  <- data[training.samples, ]
test.data <- data[-training.samples, ]
```


Perform a logistic regression as baseline model
```{r}
log_base <- glm(is_canceled ~ . - reserved_room_type.P - assigned_room_type.P, data = train.data)
summary(log_base)
vif <- vif(log_base)
vif <- data.frame(vif)
vif$Vars <- row.names(vif)
vif <- sqldf("SELECT * FROM vif
             WHERE vif < 5")

```

```{r}
data1 <- data %>%
  dplyr::select(-c(reserved_room_type.P, assigned_room_type.P))
```

```{r}
set.seed(17)
folds <- createFolds(y = data1[,2],k = 4)
```


```{r}
max=0
num=0
rmse_log1 <- as.numeric()
kappa_log1 <- as.numeric()
auc_log1 <- as.numeric()
F1_test_log1 <- as.numeric()
F1_train_log1 <- as.numeric()
for(i in 1:4) {
fold_test <- data1[folds[[i]],] #取folds[[i]]作为测试集
fold_train <- data1[-folds[[i]],] # 剩下的数据作为训练集
fold_pre <- glm(is_canceled ~ hotel + lead_time + stays_in_weekend_nights + stays_in_week_nights + adults + children + babies + is_repeated_guest + previous_cancellations + previous_bookings_not_canceled + booking_changes + days_in_waiting_list + adr + required_car_parking_spaces + total_of_special_requests + arrival_date_month.April + arrival_date_month.August + arrival_date_month.December + arrival_date_month.February + arrival_date_month.July + arrival_date_month.June + arrival_date_month.March + arrival_date_month.May + arrival_date_month.November + arrival_date_month.October + arrival_date_month.September + Meal.BB + Meal.FB + Meal.HB + Market.Complementary + reserved_room_type.B + reserved_room_type.C + reserved_room_type.D + reserved_room_type.E + reserved_room_type.F + reserved_room_type.L + assigned_room_type.B + assigned_room_type.C + assigned_room_type.D + assigned_room_type.E + assigned_room_type.F + assigned_room_type.I + assigned_room_type.K + assigned_room_type.L + deposit_type.Non_Refund + deposit_type.Refundable + customer_type.Group, data=fold_train, family = binomial)
fold_predict_test <- predict(fold_pre,type='response',newdata=fold_test)
fold_predict_test <- ifelse(fold_predict_test > 0.5, 1, 0)
fold_predict_train <- predict(fold_pre,type='response',newdata=fold_train)
fold_predict_train <- ifelse(fold_predict_train > 0.5, 1, 0)
auc_log1 <- append(auc_log1, as.numeric(auc(as.numeric(fold_test[,2]), fold_predict_test)))
kappa_log1 <- append(kappa_log1, confusionMatrix(as.factor(fold_test[,2]), as.factor(fold_predict_test))$overall['Kappa'])
#rmse
RSS <- sum((fold_test[,2] - fold_predict_test)^2)
MSE <- RSS/nrow(fold_test)
rmse_log1 <- append(rmse_log1, MSE^0.5)
#F1
F1_test_log1 <- append(F1_test_log1, as.numeric(F1_Score(as.factor(fold_test[,2]), as.factor(fold_predict_test), positive = 1)))
F1_train_log1 <- append(F1_train_log1, as.numeric(F1_Score(as.factor(fold_train[,2]), as.factor(fold_predict_train), positive = 1)))
}
print(mean(auc_log1))
print(mean(kappa_log1))
print(mean(rmse_log1))
print(mean(F1_test_log1))
print(mean(F1_train_log1))
```




Backward Stepwise Regression

```{r}
set.seed(123)
training.samples <- data1$is_canceled %>% 
  createDataPartition(p = 0.8, list = FALSE)
train.data  <- data1[training.samples, ]
test.data <- data1[-training.samples, ]
```


```{r}
regfit.bwd <- regsubsets(is_canceled ~ ., data = train.data, nvmax = 58, method = 'backward')
summary(regfit.bwd)
sum.regfit_bwd <- summary(regfit.bwd)
#sum.regfit_bwd$which
```

```{r}
which.min(sum.regfit_bwd$bic)
coef(regfit.bwd, 42)
which.min(sum.regfit_bwd$cp)
coef(regfit.bwd, 50)
which.max(sum.regfit_bwd$adjr2)
coef(regfit.bwd, 52)
```


BIC
```{r}
max=0
num=0
rmse_log_bic <- as.numeric()
kappa_log_bic <- as.numeric()
auc_log_bic <- as.numeric()
F1_test_log_bic <- as.numeric()
F1_train_log_bic <- as.numeric()
for(i in 1:4) {
fold_test <- data1[folds[[i]],] #取folds[[i]]作为测试集
fold_train <- data1[-folds[[i]],] # 剩下的数据作为训练集
log_bic <- glm(is_canceled ~ hotel + lead_time + stays_in_weekend_nights + stays_in_week_nights + adults + children + babies + previous_cancellations + previous_bookings_not_canceled + booking_changes + adr + required_car_parking_spaces+ total_of_special_requests + arrival_date_month.December + arrival_date_month.February + arrival_date_month.June + arrival_date_month.March + arrival_date_month.September + Meal.HB + Market.Complementary + Market.Direct + Market.Offline_TA_TO + Market.OnlineTA + reserved_room_type.B + reserved_room_type.C + reserved_room_type.D + reserved_room_type.E + reserved_room_type.F + reserved_room_type.G + reserved_room_type.H + assigned_room_type.B + assigned_room_type.C + assigned_room_type.D + assigned_room_type.E + assigned_room_type.F + assigned_room_type.G + assigned_room_type.H + assigned_room_type.I + assigned_room_type.K + deposit_type.Non_Refund + customer_type.Transient + customer_type.Transient_Party, data = fold_train, family = "binomial")
fold_predict_test <- predict(log_bic,type='response',newdata=fold_test)
fold_predict_test <- ifelse(fold_predict_test > 0.5, 1, 0)
fold_predict_train <- predict(log_bic,type='response',newdata=fold_train)
fold_predict_train <- ifelse(fold_predict_train > 0.5, 1, 0)
auc_log_bic <- append(auc_log_bic, as.numeric(auc(as.numeric(fold_test[,2]), fold_predict_test)))
kappa_log_bic <- append(kappa_log_bic, confusionMatrix(as.factor(fold_test[,2]), as.factor(fold_predict_test))$overall['Kappa'])
#rmse
RSS <- sum((fold_test[,2] - fold_predict_test)^2)
MSE <- RSS/nrow(fold_test)
rmse_log_bic <- append(rmse_log_bic, MSE^0.5)
#F1
F1_test_log_bic <- append(F1_test_log_bic, as.numeric(F1_Score(as.factor(fold_test[,2]), as.factor(fold_predict_test), positive = 1)))
F1_train_log_bic <- append(F1_train_log_bic, as.numeric(F1_Score(as.factor(fold_train[,2]), as.factor(fold_predict_train), positive = 1)))
}
print(mean(auc_log_bic))
print(mean(kappa_log_bic))
print(mean(rmse_log_bic))
print(mean(F1_test_log_bic))
print(mean(F1_train_log_bic))
```

CP
```{r}
max=0
num=0
rmse_log_cp <- as.numeric()
kappa_log_cp <- as.numeric()
auc_log_cp <- as.numeric()
F1_test_log_cp <- as.numeric()
F1_train_log_cp <- as.numeric()
for(i in 1:4) {
fold_test <- data1[folds[[i]],] #取folds[[i]]作为测试集
fold_train <- data1[-folds[[i]],] # 剩下的数据作为训练集
log_cp <- glm(is_canceled ~ hotel + lead_time + stays_in_weekend_nights + stays_in_week_nights + adults + children + babies + is_repeated_guest + previous_cancellations + previous_bookings_not_canceled + booking_changes + days_in_waiting_list + adr + required_car_parking_spaces + total_of_special_requests + arrival_date_month.August + arrival_date_month.December + arrival_date_month.February + arrival_date_month.July + arrival_date_month.June + arrival_date_month.March + arrival_date_month.May + arrival_date_month.September + Meal.FB + Meal.HB + Market.Complementary + Market.Direct + Market.Offline_TA_TO + Market.OnlineTA + reserved_room_type.B + reserved_room_type.C + reserved_room_type.D + reserved_room_type.E + reserved_room_type.F + reserved_room_type.G + reserved_room_type.H + assigned_room_type.B + assigned_room_type.C + assigned_room_type.D + assigned_room_type.E + assigned_room_type.F + assigned_room_type.G + assigned_room_type.H + assigned_room_type.I + assigned_room_type.K + assigned_room_type.L + deposit_type.Non_Refund + customer_type.Group + customer_type.Transient + customer_type.Transient_Party, data = fold_train, family = "binomial")
fold_predict_test <- predict(log_cp,type='response',newdata=fold_test)
fold_predict_test <- ifelse(fold_predict_test > 0.5, 1, 0)
fold_predict_train <- predict(log_cp,type='response',newdata=fold_train)
fold_predict_train <- ifelse(fold_predict_train > 0.5, 1, 0)
auc_log_cp <- append(auc_log_cp, as.numeric(auc(as.numeric(fold_test[,2]), fold_predict_test)))
kappa_log_cp <- append(kappa_log_cp, confusionMatrix(as.factor(fold_test[,2]), as.factor(fold_predict_test))$overall['Kappa'])
#rmse
RSS <- sum((fold_test[,2] - fold_predict_test)^2)
MSE <- RSS/nrow(fold_test)
rmse_log_cp <- append(rmse_log_cp, MSE^0.5)
#F1
F1_test_log_cp <- append(F1_test_log_cp, as.numeric(F1_Score(as.factor(fold_test[,2]), as.factor(fold_predict_test), positive = 1)))
F1_train_log_cp <- append(F1_train_log_cp, as.numeric(F1_Score(as.factor(fold_train[,2]), as.factor(fold_predict_train), positive = 1)))
}
print(mean(auc_log_cp))
print(mean(kappa_log_cp))
print(mean(rmse_log_cp))
print(mean(F1_test_log_cp))
print(mean(F1_train_log_cp))
```

adjr2
```{r}
max=0
num=0
rmse_log_adjr2 <- as.numeric()
kappa_log_adjr2 <- as.numeric()
auc_log_adjr2 <- as.numeric()
F1_test_log_adjr2 <- as.numeric()
F1_train_log_adjr2 <- as.numeric()
for(i in 1:4) {
fold_test <- data1[folds[[i]],] #取folds[[i]]作为测试集
fold_train <- data1[-folds[[i]],] # 剩下的数据作为训练集
log_adj2 <- glm(is_canceled ~ hotel + lead_time + stays_in_weekend_nights + stays_in_week_nights + adults + children + babies + is_repeated_guest + previous_cancellations + previous_bookings_not_canceled + booking_changes + days_in_waiting_list + adr + required_car_parking_spaces + total_of_special_requests + arrival_date_month.August + arrival_date_month.December + arrival_date_month.February + arrival_date_month.July + arrival_date_month.June + arrival_date_month.March + arrival_date_month.May + arrival_date_month.October + arrival_date_month.September + Meal.FB + Meal.HB + Market.Complementary + Market.Corporate + Market.Direct + Market.Offline_TA_TO + Market.OnlineTA + reserved_room_type.B + reserved_room_type.C + reserved_room_type.D + reserved_room_type.E + reserved_room_type.F + reserved_room_type.G + reserved_room_type.H + assigned_room_type.B + assigned_room_type.C + assigned_room_type.D + assigned_room_type.E + assigned_room_type.F + assigned_room_type.G + assigned_room_type.H + assigned_room_type.I + assigned_room_type.K + assigned_room_type.L + deposit_type.Non_Refund + customer_type.Group + customer_type.Transient + customer_type.Transient_Party, data = fold_train, family = "binomial")
fold_predict_test <- predict(log_adj2,type='response',newdata=fold_test)
fold_predict_test <- ifelse(fold_predict_test > 0.5, 1, 0)
fold_predict_train <- predict(log_adj2,type='response',newdata=fold_train)
fold_predict_train <- ifelse(fold_predict_train > 0.5, 1, 0)
auc_log_adjr2 <- append(auc_log_adjr2, as.numeric(auc(as.numeric(fold_test[,2]), fold_predict_test)))
kappa_log_adjr2 <- append(kappa_log_adjr2, confusionMatrix(as.factor(fold_test[,2]), as.factor(fold_predict_test))$overall['Kappa'])
#rmse
RSS <- sum((fold_test[,2] - fold_predict_test)^2)
MSE <- RSS/nrow(fold_test)
rmse_log_adjr2 <- append(rmse_log_adjr2, MSE^0.5)
#F1
F1_test_log_adjr2 <- append(F1_test_log_adjr2, as.numeric(F1_Score(as.factor(fold_test[,2]), as.factor(fold_predict_test), positive = 1)))
F1_train_log_adjr2 <- append(F1_train_log_adjr2, as.numeric(F1_Score(as.factor(fold_train[,2]), as.factor(fold_predict_train), positive = 1)))
}
print(mean(auc_log_adjr2))
print(mean(kappa_log_adjr2))
print(mean(rmse_log_adjr2))
print(mean(F1_test_log_adjr2))
print(mean(F1_train_log_adjr2))
```

Perform a ridge Regression
```{r}
y <- as.numeric(data1$is_canceled)
table(y)
x <- model.matrix(is_canceled ~ ., data = data1)[,-1]
```

```{r}
training.samples <- data1$is_canceled %>% 
  createDataPartition(p = 0.8, list = FALSE)
x.train <- x[training.samples,]
y.train <- y[training.samples]
x.test <- x[-training.samples,]
y.test <- y[-training.samples]
```

```{r}
# Using cross validation glmnet
lambdas <- 10^seq(2, -3, by = -.1)
ridge.mod <- glmnet(x.train, y.train, alpha=0, family = 'binomial',lambda = lambdas)
plot(ridge.mod, xvar="lambda", label = T)
coef(ridge.mod)[,10]
probabilities <- ridge.mod %>% predict(newx = x.test)
predicted.classes <- ifelse(probabilities > 0.5, 1, 0)
SSE <- sum((predicted.classes - y.test)^2)
RMSE <- sqrt(SSE/nrow(x.test))
RMSE
```

```{r}
cv_ridge <- cv.glmnet(x.train, y.train, alpha = 0, lambda = lambdas)
optimal_lambda <- cv_ridge$lambda.min
optimal_lambda
```


```{r}
ridge.mod1 <- glmnet(x.train, y.train, alpha=0, family = 'binomial', lambda = 0.001)
#plot(ridge.mod1, xvar="lambda", label = T, xlim(-4,7))
coef(ridge.mod1)[,1]
probabilities1 <- ridge.mod1 %>% predict(newx = x.test)
predicted.classes1 <- ifelse(probabilities1 > 0.5, 1, 0)
SSE1 <- sum((predicted.classes1 - y.test)^2)
RMSE1<- sqrt(SSE1/nrow(x.test))
RMSE1
```

```{r}
varImp(ridge.mod1,lambda = ridge.mod1$lambda)
ridgeImp <- data.frame(varImp(ridge.mod1, lambda = ridge.mod1$lambda))
ridgeImp$Vars <- row.names(ridgeImp)
ggplot(ridgeImp, aes(x = reorder(ridgeImp$Vars, ridgeImp$Overall), y = ridgeImp$Overall)) + geom_bar(stat = "identity", fill = 'Lightblue') + coord_flip()
ridge_data <- sqldf("SELECT * FROM ridgeImp
      ORDER BY Overall DESC")
#write_csv(ridge_data, "ridge_result.csv")
```

```{r}
max=0
num=0
rmse_log_rid <- as.numeric()
kappa_log_rid <- as.numeric()
auc_log_rid <- as.numeric()
F1_test_log_rid <- as.numeric()
F1_train_log_rid <- as.numeric()
for(i in 1:4) {
fold_test <- data1[folds[[i]],] #取folds[[i]]作为测试集
fold_train <- data1[-folds[[i]],] # 剩下的数据作为训练集
log_rid <- glm(is_canceled ~ previous_cancellations + required_car_parking_spaces + adr + previous_bookings_not_canceled + adults + booking_changes + deposit_type.Non_Refund + assigned_room_type.L + assigned_room_type.I + total_of_special_requests + lead_time + reserved_room_type.G + children + stays_in_week_nights + assigned_room_type.K + assigned_room_type.H + assigned_room_type.E + reserved_room_type.E + reserved_room_type.F + reserved_room_type.H + assigned_room_type.C + assigned_room_type.D + reserved_room_type.L + reserved_room_type.C + reserved_room_type.D + stays_in_weekend_nights + customer_type.Transient + Market.OnlineTA	+ Market.Offline_TA_TO + assigned_room_type.B + reserved_room_type.B + Meal.FB + Market.Direct + days_in_waiting_list + is_repeated_guest + 
                 customer_type.Group + arrival_date_month.July + Market.Complementary + arrival_date_month.September + customer_type.Transient_Party + 
                 arrival_date_month.August + arrival_date_month.June + deposit_type.Refundable + arrival_date_month.March + Meal.HB + hotel + arrival_date_month.May + 
                 arrival_date_month.December + arrival_date_month.February, data = fold_train, family = "binomial")
fold_predict_test <- predict(log_rid,type='response',newdata=fold_test)
fold_predict_test <- ifelse(fold_predict_test > 0.5, 1, 0)
fold_predict_train <- predict(log_rid,type='response',newdata=fold_train)
fold_predict_train <- ifelse(fold_predict_train > 0.5, 1, 0)
auc_log_rid <- append(auc_log_rid, as.numeric(auc(as.numeric(fold_test[,2]), fold_predict_test)))
kappa_log_rid <- append(kappa_log_rid, confusionMatrix(as.factor(fold_test[,2]), as.factor(fold_predict_test))$overall['Kappa'])
#rmse
RSS <- sum((fold_test[,2] - fold_predict_test)^2)
MSE <- RSS/nrow(fold_test)
rmse_log_rid <- append(rmse_log_rid, MSE^0.5)
#F1
F1_test_log_rid <- append(F1_test_log_rid, as.numeric(F1_Score(as.factor(fold_test[,2]), as.factor(fold_predict_test), positive = 1)))
F1_train_log_rid <- append(F1_train_log_rid, as.numeric(F1_Score(as.factor(fold_train[,2]), as.factor(fold_predict_train), positive = 1)))
}
print(mean(auc_log_rid))
print(mean(kappa_log_rid))
print(mean(rmse_log_rid))
print(mean(F1_test_log_rid))
print(mean(F1_train_log_rid))
```

+ Market.Direct + days_in_waiting_list + is_repeated_guest + customer_type.Group + arrival_date_month.July + Market.Complementary + arrival_date_month.September + customer_type.Transient_Party + arrival_date_month.August + arrival_date_month.June + deposit_type.Refundable + arrival_date_month.March + Meal.HB + hotel + arrival_date_month.May + arrival_date_month.December + arrival_date_month.February







